Modelling single-cell dynamics\\with trajectories and gene regulatory networks

### 2019-11-24 defence_internal/pres_v1.tex
~

\begin{frame}
	\frametitle{Research questions regarding single-cell biology}
	\begin{center}
		\only<1>{\includegraphics[width=\linewidth]{figures/11a_fundamental.pdf}}%
		\only<2>{\includegraphics[width=\linewidth]{figures/11b_fundamental.pdf}}%
		\only<3>{\includegraphics[width=\linewidth]{figures/11c_fundamental.pdf}}%
		\only<4>{\includegraphics[width=\linewidth]{figures/11d_fundamental.pdf}}%
		\only<5>{\includegraphics[width=\linewidth]{figures/11e_fundamental.pdf}}%
		\only<6>{\includegraphics[width=\linewidth]{figures/11f_fundamental.pdf}}%
	\end{center}
\end{frame}

@@

@@

>>>>

\begin{frame}
	\frametitle{Research questions regarding single-cell biology}
	\begin{center}
		\only<1>{\includegraphics[width=\linewidth]{figures/11a_fundamental.pdf}}%
		\only<2>{\includegraphics[width=\linewidth]{figures/11b_fundamental.pdf}}%
		\only<3>{\includegraphics[width=\linewidth]{figures/11c_fundamental.pdf}}%
		\only<4>{\includegraphics[width=\linewidth]{figures/11d_fundamental.pdf}}%
		\only<5>{\includegraphics[width=\linewidth]{figures/11e_fundamental.pdf}}%
	\end{center}
\end{frame}

@@

%\begin{frame}
%	\frametitle{dyngen: Benchmarking with \textit{in silico} cells}
%	\begin{center}
%		\includegraphics[width=.6\linewidth]{figures/end_part_dyngen.pdf}
%	\end{center}
%	\topright{ch2}
%\end{frame}

@@

\begin{frame}
	\includegraphics[width=\linewidth]{figures/overview.pdf}
\end{frame}

%%%%%%%%%%%%%%%%%%% EXTRA
\begin{frame}
	\vfill
	\begin{center}
		\color{mygray}
		{\LARGE Extra slides} 
	\end{center}
	\vfill
\end{frame}

\begin{frame}
	\frametitle{Sample-specific network inference}
	\begin{center}
		\only<1>{\includegraphics[width=.7\linewidth]{figures/extra_bred1_simplify.pdf}}%
		\only<2>{\includegraphics[width=\linewidth]{figures/extra_bred2a_fimp.pdf}}%
		\only<3>{\includegraphics[width=\linewidth]{figures/extra_bred2b_fimp.pdf}}%
		\only<4>{\includegraphics[width=\linewidth]{figures/extra_bred2c_fimp.pdf}}%
		\only<5>{\includegraphics[width=\linewidth]{figures/extra_bred2d_fimp.pdf}}%
		\only<6>{\includegraphics[width=\linewidth]{figures/extra_bred2e_fimp.pdf}}%
		\only<7>{\includegraphics[width=\linewidth]{figures/extra_bred2f_fimp.pdf}}%
		\only<8>{\includegraphics[width=\linewidth]{figures/extra_bred2g_fimp.pdf}}%
		\only<9>{\includegraphics[width=\linewidth]{figures/extra_bred2h_fimp.pdf}}%
		\only<10>{\includegraphics[width=\linewidth]{figures/extra_bred2i_fimp.pdf}}%\\
		\only<11>{\includegraphics[width=\linewidth]{figures/extra_bred2j_fimp.pdf}}%
		\only<12>{\includegraphics[width=\linewidth]{figures/extra_bred2k_fimp.pdf}}%
		\only<13>{\includegraphics[width=\linewidth]{figures/extra_bred2l_fimp.pdf}}%
	\end{center}
	\topright{ch6}
\end{frame}
